\LARGE Untangling the link between traits, size and growth rate in plants

### 2015-11-19 fitting.Rmd
Use remake's download targets
Removes downloader dependency, simplifies code a bit.
Update to reflect upstream breaking changes in plant
- renaming plant physiology from FFW16 -> FF16
- renaming solver from EBT to SCM (capturing correct method used)
- Introduced at traitecoevo/plant/commit/bf4208066e8f83c31ced90435cc3744b5ea97df6

# Fitting TREE to observed data

@@

```{r, echo=TRUE, results="hide"}
library(tree2)

# given a dbh x, traits and parameters, grows plant to right size and estimates growth rate
run_tree <- function(x, E=1, traits=list(), pars=list(),
                     strategy=default_strategy()) {
  strategy[names(traits)] <- traits
  strategy[names(pars)] <- pars
  pp <- grow_plant_to_size(Plant(strategy), x, "diameter",
                           fixed_environment(E))
  sapply(pp$plant, function(p) p$vars_growth[["dbasal_diam_dt"]])
}
```
We can test it works

>>>>

# Fitting plant to observed data

@@

```{r, echo=TRUE, results="hide"}
library(plant)

# given a dbh x, traits and parameters, grows plant to right size and estimates growth rate
run_tree <- function(x, E=1, traits=list(), pars=list(),
                     strategy=default_strategy()) {

  x <- c(0.005, 0.01)

  env <- fixed_environment(1)
  pl <- run_plant_to_sizes(x, "diameter", strategy, env, time_max=3000)

  strategy=FF16_Strategy()
  env <- fixed_environment(1)  
  pl <- FF16_PlantPlus(strategy)
  res <- grow_plant_to_size(pl, x, "diameter", env, time_max=3000)

  x <- seq(FF16_Plant(strategy)$height, strategy$hmat, length.out=100)
  env <- fixed_environment(canopy_openness)
  run_plant_to_sizes(heights, "height", strategy, env, time_max=300)

  pl <- FF16_PlantPlus(strategy)
  res <- grow_plant_to_size(pl, sizes, size_variable, env, time_max,
                            warn=FALSE, filter=filter)

run_plant_to_sizes

  strategy[names(traits)] <- traits
  strategy[names(pars)] <- pars
  pp <- grow_plant_to_size(pl, x, "diameter",
                           fixed_environment(E))
  sapply(pp$plant, function(p) p$vars_growth[["dbasal_diam_dt"]])
}
```
We can test it works
